SNEQ_Lynott_example

### 2017-10-21 NSEQ_Lynott_example.Rmd
Fixed direction of the odds ratio test from hot/cold to cold/hot, to match the test in Lynott et al.

#  We can now run the TOST!
tost <- TOSTtwo.prop(prop1 = selfish.hot, 
                     prop2 = selfish.cold, 
                     n1    = n.hot, 
                     n2    = n.cold, 
                     low_eqbound  = -crit.diff, 
                     high_eqbound = crit.diff, 
                     alpha = 0.05)

>>>>

#  We can now run the TOST!
tost <- TOSTtwo.prop(prop1 = selfish.cold, 
                     prop2 = selfish.hot, 
                     n1    = n.cold, 
                     n2    = n.hot, 
                     low_eqbound  = -crit.diff, 
                     high_eqbound = crit.diff, 
                     alpha = 0.05)
